SpecHunter: Interactively Inferring Taint Specifications Using Bayes Net

### 2021-04-04 My-Papers/SpecHunter/overview.tex
started writing information propagation

% 'incoming edge가 너무 많아서도, 너무 적어서도 안 된다.'
Next, we control the number of incoming edges of each node. It is already
mentioned that the size of a node's CPT is exponential to the number of its
parent nodes. To our empirical knowledge, if the number of incoming edges (hence
the number of parent nodes) becomes more than 6, the process of converting the
graph into a Bayesian network becomes drastically intractable. Therefore, we
reduce the number of parents of such ``rich nodes'' by making the parents of the
rich node shoot a similarity edge not to the rich node in question, but to some
other node that is not yet rich.

@@

After all these preprocessing, we are finally ready to turn chopped graphs into
small, yet full-blown Bayesian networks.

@@

Here, we expound on the core inference algorithm. The inference algorithm is
largely

>>>>

Next, we control the number of incoming edges of each node. It is already
mentioned that the size of a node's CPT is exponential to the number of its
parent nodes. To our empirical knowledge, if the number of incoming edges (hence
the number of parent nodes) becomes more than 6, the process of converting the
graph into a Bayesian network becomes drastically intractable. Therefore, we
reduce the number of parents of such ``rich nodes'' by making the parents of the
rich node shoot a similarity edge not to the rich node in question, but to some
other node that is not yet rich.

@@

After all these preprocessing, we are finally ready to turn chopped graphs into
small, yet full-blown Bayesian networks. Each node corresponds to a random
variable $\text{The taint specification of method} M$, whose possible values are
$source$, $sink$, $sanitizer$, and $none$. Now, they are waiting for an external
oracle to instantiate its value to one of these four.

@@

Here, we expound on the core inference algorithm. Inference on the Bayesian
network is divided into two parts: local propagation and global propagation.
Local propagations pass information given by the oracle within a single graph,
whereas global propagations pass the information from one graph to another.
